### 2022-12-20 README.Rmd
code restyle

diag(cmat) <- c(10,11,13)
cmat[upper.tri(cmat)] <- 3:5
cmat[lower.tri(cmat)] <- 3:5

@@

```{r fit-polymod}
set.seed(2022-09-06)
contact_model <- fit_single_contact_model(
  contact_data = polymod_contact_data,
  population = polymod_survey_data
  )
```

@@

```{r predict-contacts}
set.seed(2022-09-06)
synthetic_contact_fairfield <- predict_contacts(
  model = contact_model,
  population = fairfield_age_pop,
  age_breaks = c(seq(0, 85, by = 5), Inf)
)

>>>>

diag(cmat) <- c(10, 11, 13)
cmat[upper.tri(cmat)] <- 3:5
cmat[lower.tri(cmat)] <- 3:5

@@

```{r fit-polymod}
set.seed(2022 - 09 - 06)
contact_model <- fit_single_contact_model(
  contact_data = polymod_contact_data,
  population = polymod_survey_data
)
```

@@

```{r predict-contacts}
set.seed(2022 - 09 - 06)
synthetic_contact_fairfield <- predict_contacts(
  model = contact_model,
  population = fairfield_age_pop,
  age_breaks = c(seq(0, 85, by = 5), Inf)
)
